Imm algorithm implementation for tracking

### 2020-01-30 Latex/exp.tex
zzzz

\title{Imm algorithm implementation for tracking}
\author{
Paiola Lorenzo 000000

@@

\section*{Introduction}
\justify
The porpouse of this document is the analysis and performance evaluation of an IMM algorithm's implementation in
a sensor grid tracking an object. The object can move with two different model, random walk and unicycle, governed by
 a Markov chain. The goal is evaluate the best trade-off between error on estimated position and real position and number of 
 messagesses involved in tracking

\begin{multicols}{2}
    \section*{Backgound}
    \justify
        Tracking a object with a changing dynamic require propers algorithms and filters. Retriving physical data with
        observations it's not enough, models achiving the best-fit to our data is needed in order to make a prediction and estimate 
        with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
        from sensor are combined with different dynamical models through the algorithm... 
        \subsection*{Sensor in simulation model}
            The target can move with random movement described by a Markov chain and accordingly two different models of movement
            The tracking are performed with grid of sensors. In order to perform a proper simulation the sensor has assumed to have a limited
            range for the tracking and we cannot retrive any information if target is out. It also took in consideration the power consumption 
            for a possible physical system: to model a more enegy efficient system the sensor can switch to 3 different working condition: On,Off,Idle.
            To achive this goal the sensor is working as a state machine as showned in the figure below: 
                \begin{figure}[h!]
                \centering
                \includegraphics[scale=0.05]{UntitledDiagram.png}
                \caption{State machine sensor}
                \label{fig:galaxy}
                \end{figure}
            Sensors can communicate with the sensors in their neighboorhoods and exchange signal named CanSense and CantSense that regulate the transition
            between differents state. Thus implies that not all the sensors receive all the messagge, but only from their Neighboors. The sensors in On state
            create a fully connected graph. The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
            sensors turned on depends on working range choosed and position of target. The mechanism that regulate the transition from sensors state 
            relay on the information exchanged with nearby sensor. Different state can receive and send different messagesses. A sensor in On state has the moving 
            object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle. 
            Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
            if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
            A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
            can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step. 
            When a sensor have the target in range it does a measure operation each timestep. the sensor works a radar in this model and remembering
            \begin{equation}
                z(k)=H(k)x(k)+\textbf{R}
            \end{equation}
            where the \textbf{H} is 
            \begin{equation}
                H= \begin{bmatrix}
                    dopo & la \\
                    scr & vo \\
                \end{bmatrix}
            \end{equation} 
        \subsection*{Imm and Linear Consensu}
               The IMM algorithm is based on the

@@

    \subsection*{Random walk and Unycicle model}
    The target in this simulation can move accordingly to two model: random walk and Unycicle. Each of this model has a Markov chain that 
    regulate how the given input goes in the system. For the random walk we have 5 state: costant velocity, positive or negative acceleration
     on x direction and positive or negative deceleration on y direction. So the input are $\ddot{x}$ and $\ddot{y}$. The Markov chain associate is a circulant matrix as showned below
     $$\begin{vmatrix}
         0.8 & 0.025 & 0.025 & 0.025 & 0.025 // 
     \end{vmatrix}$$
     The equation regulating the state of the system is as well know
    \begin{equation}
    X^{+}= \textbf{A}X(k) + \textbf{B}u(k) + \textbf{G}w(k)
    \end{equation}
    The Random walk model has is a linear model. State,state and noise matrix associate to the random walk has showned below:
    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
        1&0&\delta&0\\
        0&1&0&\delta\\
        0&0&1&0\\
        0&0&0&1\\
        \end{bmatrix}
        G=\begin{bmatrix}
            \delta^2/2&0\\
            0&\delta^2/2\\
            \delta&0\\
            0&\delta\\
            \end{bmatrix}
        \]
        The \textbf{B} input matrix change accordingly with the acceleration input
    \[
        B=\begin{bmatrix}
            \delta^2/2 & 0\\
            0 & 0  \\
            \delta & 0 \\
            0 & 0 \\
            \end{bmatrix}
            B=\begin{bmatrix}
                0 & 0 \\
             0 & \delta^2/2 \\
            0 & 0 \\
            0 & \delta \\
            \end{bmatrix}
  \]
  It can be noticed that the \textbf{G} matrix of error can be seen as a sum of positive \textbf{B} rescaled by a random factor.

  The unycicle model has different input and state description. The inputare represente by the angular acceleration of the wheel and the steering angle acceleration.
  possible state are 5: constant angular velocity, acceleration and deceleration of the wheel and positice or negative acceleration of the steering angle.
  The associate Markov chain for this case is  
   $$\begin{vmatrix}
         0.8 & 0.025 & 0.025 & 0.025 & 0.025 // 
     \end{vmatrix}$$
   Unycicle model instead is a Non-linear model. Thus is necessary to use a linearization in the Kalman filter implementation
   The matrix that represent the state of system for this case are
    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
   1&0&\delta&0\\
   0&1&0&\delta\\
   0&0&1&0\\
   0&0&0&1\\
   \end{bmatrix}
   G=\begin{bmatrix}
       \delta^2/2&0\\
       0&\delta^2/2\\
       \delta&0\\
       0&\delta\\
       \end{bmatrix}
   \]
    \subsection*{Data's simulation}

>>>>

\title{Imm algorithm implementation for tracking}
\author{
Paiola Lorenzo 198573

@@

\section*{Introduction}
\justify
The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
agent's traking. The agent switches between linked models of movement by the means of a Markov chain. The goal is evaluate the best trade-off
between error on estimated position and real position and number of messagesses involved in the tracking.

\begin{multicols}{2}
    \section*{Setting}
    \justify
    NON CAPISCO COSA VUOI DIRE, IN QUALSIASI CASO QUA AGGIUNGI CHE PARLIAMO DI FILTRI DA DISCRETE-DISCRETE
    \\
    Tracking an object with a switching dynamic require proper algorithms and filters.Retriving physical data with
    observations it's not enough in the case of Markov processes that switch between modes and we need to
    , models achiving the best-fit to our data is needed in order to make a prediction and estimate
    with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
    from sensor are combined with different dynamical models through the algorithm...
    \subsection*{Sensor's model}
    The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep and
    are disposed as a uniform grid. In order to simulate the real workings of a sensor, we have limited the range of measurement to the distance
    between one sensor and the following one in any direction in the grid, as soon as the agent exceed the range the device will stop sensing.
    This property of the sensor grid, coupled by its geometry, ensures that no more than 4 sensors can measure the agent position at the time,
    so it made sense to let sensor switch between 3 different states that we named ON, OFF and IDLE. This can be justified as a way to make the system
    more power efficient and to avoid useless data stream towards sensors that aren't currently in range.
    The sensor is modeled as a state machine as shown.
    \\
    AGGIUSTA FIGURA CHE E' SBAGLIATA E NON CI SONO GLI INRANGE, I CANSENSE/CANNOT SONO I SEGNALI MANDATI, NON LE ROBE CHE FANNO CAMBIARE STATO 
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.05]{UntitledDiagram.png}
        \caption{State machine sensor}
        \label{fig:galaxy}
    \end{figure}
    \\
    TABELLA CON LE FUNZIONI DEGLI STATI (mettere di fianco al paragrafo sotto una immagine che fa  vederecosa intendiamo con neighboors (gli 8 
    sensori circostanti))
    \\
    Sensors can communicate with the devices adjacent to them (Neighboorhood) and exchange with them signals named CanSense and CantSense
    which state respectively whenever the agent gets in or goes out of the communicating sensor's range. This check is done through the 
    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure before.
    \\
    QUESTO METTILO NEL CONSENSUS, NON HA SENSO PARLARNE QUI
    \\
    The set of active sensors is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
    more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
    sensors as fully-connected, since the distance between them is short and they are directly linked.
    \\
    The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
    sensors turned on depends on working range choosed and position of target. The mechanism that regulate the transition from sensors state
    relay on the information exchanged with nearby sensor. Different state can receive and send different messagesses. A sensor in On state has the moving
    object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle.
    Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
    if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
    A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
    can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step.
    When a sensor have the target in range it does a measure operation each timestep. the sensor works a radar in this model and remembering
    \begin{equation}
        z(k)=H(k)x(k)+\textbf{R}
    \end{equation}
    where the \textbf{H} is
    \begin{equation}
        H= \begin{bmatrix}
            dopo & la \\
            scr  & vo \\
        \end{bmatrix}
    \end{equation}
    \subsection*{Imm and Linear Consensu}
    The IMM algorithm is based on the

@@

    \subsection*{Random walk and Unycicle model}
    The target in this simulation can move accordingly to two families of models, both are Markov processes.
    \\
    TABELLA CON DA UNA PARTE LE MODES DI UNO E DELL'ALTRO AL POSTO DI SPIEGARLO A PAROLE
    \\
    Each of this model has a Markov chain that
    regulate how the given input goes in the system. For the random walk we have 5 state: costant velocity, positive or negative acceleration
    on x direction and positive or negative deceleration on y direction. So the input are $\ddot{x}$ and $\ddot{y}$. The Transition matrix 
    associated with the Markov's chain is shown below
    $$\begin{vmatrix}
            0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
        \end{vmatrix}$$
    The linear system describing the evolution of the state is 
    \begin{equation}
        X^{+}= \textbf{A}X(k) + \textbf{B}u(k) + \textbf{G}w(k)
    \end{equation}
    State,state and noise matrix associate to the random walk has shown below:
    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
            1 & 0 & \delta & 0      \\
            0 & 1 & 0      & \delta \\
            0 & 0 & 1      & 0      \\
            0 & 0 & 0      & 1      \\
        \end{bmatrix}
        G=\begin{bmatrix}
            \delta^2/2 & 0          \\
            0          & \delta^2/2 \\
            \delta     & 0          \\
            0          & \delta     \\
        \end{bmatrix}
    \]
    With $\delta$ time step of the simulation.
    The \textbf{B} input matrix change accordingly with the acceleration input (of what we suppose we know only the magnitude)
    \[
        B=\begin{Bmatrix}
            \begin{bmatrix}
                0 & 0 \\
                0          & 0 \\
                0     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                \delta^2/2 & 0 \\
                0          & 0 \\
                \delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                -\delta^2/2 & 0 \\
                0          & 0 \\
                -\delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & \delta^2/2 \\
                0 & 0          \\
                0 & \delta     \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & -\delta^2/2 \\
                0 & 0          \\
                0 & -\delta     \\
            \end{bmatrix}
        \end{Bmatrix}
    \]
    The \textbf{G} matrix is a merge between the "positive" matrices .

    The unycicle model has different input and state description. The inputare represente by the angular acceleration of the wheel and the steering angle acceleration.
    possible state are 5: constant angular velocity, acceleration and deceleration of the wheel and positice or negative acceleration of the steering angle.
    The associate Markov chain for this case is
    $$\begin{vmatrix}
            0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
        \end{vmatrix}$$
    Unycicle model instead is a Non-linear model. Thus is necessary to use a linearization in the Kalman filter implementation
    The matrix that represent the state of system for this case are
    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
            1 & 0 & \delta & 0      \\
            0 & 1 & 0      & \delta \\
            0 & 0 & 1      & 0      \\
            0 & 0 & 0      & 1      \\
        \end{bmatrix}
        G=\begin{bmatrix}
            \delta^2/2 & 0          \\
            0          & \delta^2/2 \\
            \delta     & 0          \\
            0          & \delta     \\
        \end{bmatrix}
    \]
    \subsection*{Data's simulation}
